---
title: "Regression"
author: "Tarun"
date: "4/21/2021"
output: html_document
---
## Overview

Our goal here to explore the relationship between the variables of the "mtcars" dataset. Our research will focus on exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). We are particularly interested in the following two questions:

1. “Is an automatic or manual transmission better for MPG?”
2. “Quantify the MPG difference between automatic and manual transmissions.”
I am going to use the following R libraries to assist in my analysis:


```{r,echo=T}
require(datasets)
require(ggplot2)
require(GGally)
require(ggthemes)
require(plotly)
require(dplyr)
require(ggcorrplot)
require(Amelia)
require(leaps)
cars <- mtcars
head(cars)
missmap(cars) # to check the missing values
```

There is no missing values in the dataset but, we need to change some of the varible types. 


## Data Processing

```{r,echo=TRUE}
cars$cyl <- as.factor(cars$cyl)
cars$vs <- as.factor(cars$vs)
cars$am <- as.factor(cars$am)
str(cars)
```

## Exploratory Analysis 

```{r,echo=TRUE}
 # To check the correlation b/w the variables 
plot1 <- ggplotly(ggcorr(mtcars, nbreaks = 4, palette = "RdGy"))
plot1

plot2 <- ggplot(cars, aes(mpg)) + 
  geom_histogram(aes(fill=am),binwidth = 5) +facet_grid(.~am)+
  labs(title = "Histogram of Miles per Gallon",
       x='"Transmission Type: 0 = Automatic ; 1 
       = Manual"', y = "Frequency") 
   
ggplotly(plot2)



plot3 <- ggplot(data = cars, aes(x = am, y = mpg)) +
  geom_boxplot(aes(fill=factor(cyl))) +
  labs(x='"Transmission Type: 0 = Automatic ; 1 
       = Manual"',y="Miles per Gallon",
       title='MPG by Transmission Type')
ggplotly(plot3)
aggregate(mpg ~ am, data = mtcars, mean)
```

Correlation Analysis - As we can see in the correlation graph, that "Miles per Gallon"  have - correlation with cyl, hp, and wt. That means car mileage will decrease as car weight and horsepower increase.

Histogram Analysis - Manual transmission cars have higher MPG than automatic transmission.

Boxplot Analysis - Manual transmission is 7.25 MPG higher than automatic transmission.


## Regression modelling

Here I will use the Best Subset Regression method to check which variable affects the mpg more.
To run the regression with the best subset selection, we will use the regsubsets function from the package leaps

```{r,echo=T}
fit <- regsubsets(mpg~., cars, nvmax = 11)
# nvmax is the maximum number of predictors to be included in the model by default it is set to 8
sum <- summary(fit)
#to assess the goodness-of-fit we will use the adjusted R square
# because it is automatically computed for each model

sum$adjr2
which.max(sum$adjr2)# find the model with maximum adjusted R squared
coef(fit, 5) # To print the coefficients of this model


model <- lm(mpg~ cyl+hp+wt+vs+am, data=cars)# Now applying the regression model on best fit coefficients
summary(model)
```
The results suggest that the best model includes cyl6, cyl8, hp, wt, and manual variables. This model explains about 86.59% of the variance. Cylinders change negatively with mpg (-3.03miles and -2.16miles for cyl6 and cyl8, respectively), so do with horsepower (-0.03miles) and weight (-2.5miles for every 1,000lb). On the other hand, the manual transmission is 1.81mpg better than the automatic transmission.



## Conclusion

On average, the manual transmission is better than the automatic transmission by 1.81mpg. However, transmission type is not the only factor accounting for MPG; cylinders, horsepower, and weight are the important factors affecting the MPG.


